---
title: "Introduction"
author: |
    | Stephen Pederson
    | Dame Roma Mitchell Cancer Research Laboratories
    | Adelaide Medical School
    | University of Adelaide
date: "`r format(Sys.Date(), '%d %B, %Y')`"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
```

```{r packages}
library(tidyverse)
library(DiagrammeR)
library(pander)
library(yaml)
```

```{r load_funs}
source("https://raw.githubusercontent.com/steveped/spBioUtils/main/R/helpers.R")
source("https://raw.githubusercontent.com/steveped/spBioUtils/main/R/rm_dot_node.R")
source("https://raw.githubusercontent.com/steveped/spBioUtils/main/R/add_input_node.R")
source("https://raw.githubusercontent.com/steveped/spBioUtils/main/R/change_node_colour.R")
```


```{r config}
config <- here::here("config/config.yml") %>%
  read_yaml()
samples <- config$samples %>% 
  here::here() %>% 
  read_tsv()
```


## Description

This is the data setup and preparations for subsequent integration with ChIP-Seq data.
No identification of TADs is included as this workflow simply aims to identify *significant interactions* (above background) using combinations of bin sizes.

- Data was aligned to `r config$ref$build` obtained from Gencode release `r config$ref$gencode`.
- HiC Interactions were identified using [Hic-Pro v3.0.0](https://github.com/nservant/HiC-Pro/releases/tag/v3.0.0) and bins of `r pander(paste0(as.integer(str_split(config$hicpro$bin_size, pattern = " ")[[1]])/1e3, "kb"))`
- Bin pairs with numbers of interactions significantly above background were identified using [MaxHiC](https://github.com/Rassa-Gvm/MaxHiC)

## Workflow

```{r plot_workflow, fig.height = 8, fig.width = 10, fig.cap = "*Summary of processing workflow. The primary data pipeline is shown in red, with QC/reporting steps shown in orange. Preparatory steps are shown in blue whilst collation of final output is in green.*"}
here::here("rules/rulegraph.dot") %>%
  readLines() %>%
  rm_dot_node(node = "\"all\"") %>%
  add_input_node(node = "RAW DATA", col = "red", ignore = "(get|build|make|install)") %>%
  change_node_colour("(hicpro|contact|adapter|merge|run)_", "red") %>% 
  change_node_colour("collect|compress|zip|define", "forestgreen") %>% 
  change_node_colour("(reference|index|chrom_sizes|install_maxhic|find|config)", "blue") %>% 
  change_node_colour("qc|stats|lengths|rulegraph|site|pics|convert", "orange") %>% 
  str_replace_all("_", "\n") %>% 
  str_replace_all("snakemake\ndag", "snakemake_dag") %>%
  str_replace_all("fontsize=[0-9]+", "fontsize=16") %>%
  grViz()
```

